\section{Program Stubs and Test Data Required}

In this section we are presenting the drivers and stubs that have to be created
in order to test our system.
Thanks to the fact that we are using an hybrid strategy there are different
independent low-level components that do not require any driver or stub since
these components will be created before the component that needs them.

\begin{description}

\item[A populated test database:] The database has to contain a small set of
all the entities needed to the system to work properly.

\item[Account Manager Stub:] This is the stub that exposes the registration,
login and account data management functionalities. The registration of a user
simply returns the result of the registration based on the results obtained from
the \textbf{Driving License Manager} and the \textbf{Payment Manager}.

\item[Reservation Manager Stub:] This stub simulates all the possible operations
that can be done while reserving a car, for instance: reserving a car, ending a
reservation or viewing the reservation details. It can retrieve datas from the
\textbf{Fares and Policies Manager} and from the \textbf{Area Manager}.

\item[Map Manager Stub:] This stub shows the functionalities of the interactive
map displayed during the reservation process. This component can get datas from
the \textbf{Area Manager} and from the \textbf{Vehicle manager}.

\item[Maintenance Manager Stub:] This stub presents the functionalities related
to the maintenance of the cars and the different parking areas. It has to show
data relative to any malfunction that it can acqure from the
\textbf{Area Manager} and the \textbf{Vehicle Manager} components.

\end{description}

The \textbf{Driving License Manager}, the \textbf{Payment Manager}, the
\textbf{Fares and Policies Manager}, the \textbf{Area Manager} and the
\textbf{Vehicle Manager} are those independent components that are preemptively
created in order to reduce the numeber of stubs needed in the project.
