\subsubsection{Scope}

<<<<<<< HEAD
The hereby Integration Test Plan Document presents a detailed description of the integration testing plan that the development team should follow to accomplish correctly the integration testing process.
=======
This document contains a detailed description of the integration testing plan that the development team should follow to successfully complete the integration testing process.
>>>>>>> refs/remotes/origin/master

The scope of this document covers four main topics regarding the integration phase. Here, the scope is presented reflecting the main structure of the ITPD, allowing the reader to better understand what is discussed in the following sections.

\begin{itemize}
	\item \textbf{Integration Strategy:} the entry criteria, both general and specific, that must be met before the integration test take place, what are the subsystems to integrate, which integration strategies are adopted and the integration sequence to follow are deeply described and discussed, pointing out the rationale of each choice.
	\item \textbf{Individual Steps and Test Description:} the type of test performed in each step of the integration process and applied to each component and subsystem, along with the expected results, are presented.
	\item \textbf{Tools and Test Equipment:} the needed tools to perform the integration are presented, and briefly described their usage during the integration process.
	\item \textbf{Program Stubs and Test Data Required:} possible stubs/drivers or special data required to proceed in each step of the integration process are presented and described. 
\end{itemize}
