\subsection{Component interfaces}
In this sections will be presented and described all the interfaces present in
our system.

\begin{itemize}
  \item \textbf{Web Server Interface}: Our web server exposes a RESTful
                                       interface over the HTTPS protocol.
  \item \textbf{Authentication Interface}: The access to the resources of our
                                           system is mediated by this interface
                                           that verifies the identity of each
                                           client that tries to connect to our
                                           system using HTTP basic auth over
                                           HTTPS.
  \item \textbf{Registration Interface}: This is the interface that provides
                                         the registration functionalities to the
                                         client connecting to our system, it
                                         relies on a document validation service
                                         and on a payment handling service.
  \item \textbf{Login Interface}: This inteface provides the login
                                  functionality to our system, it allows three
                                  different user type: Normal User,
                                  Administrator User and Maintenance Staff.
  \item \textbf{Account Management Interface}: This inteface allows any user to
                                               edit his account data or even to
                                               remove his account from the
                                               system.
  \item \textbf{Validation Interface}: This is the interface that connects our
                                       system to the external document
                                       validation service.
  \item \textbf{Validation API}: The \textit{IDCHECK.IO} APIs are used in our
                                 system for the driving license validation.
                                 These are RESTful APIs that use JSON format.
                                 Given the picture of a driving license this
                                 service tells our system if the document is
                                 valid or not.
  \item \textbf{Payment Credential Validation Interface}: This interface
                                 connects our system to an exteral API that
                                 controls the authenticity of the payment
                                 informations submitted by the user.
  \item \textbf{Payment Service API}: The \textit{LevelUp} APIs offer a lot of
                                      features related to the payments. They
                                      use JSON format response.
  \item \textbf{Reservation Interface}: This is the interface with which a
                                        normal user interacts in order to make a
                                        reservation. It interacts with different
                                        components in order to give the user all
                                        the informations he needs to make a
                                        reservation.
  \item \textbf{Payment Interface}: This is the interface responsible for the
                                    communication between the system and the
                                    external service that handles payments.
  \item \textbf{Search Interface}: This interface allows a user to search an
                                   available car.
  \item \textbf{Areas Data Interface}: This is the iterface used to fetch all
                                       the data about the parking areas, such as
                                       their position, and in case of special
                                       parking areas, the number of available
                                       plugs.
  \item \textbf{Areas Management Interface}: This is the iterface used by the
                                             administrator users to manage all
                                             the aspects of the parking areas.
                                             They can be added, removed or
                                             modified to reflect any changes in
                                             the real world.
  \item \textbf{Fares and Policies Interface}: This interface provides all the
                                               policies and is used to retrieve
                                               the fares to apply to the rides.
  \item \textbf{Fares and Policies Management Interface}: This interface
                                       provides to an administrator user all the
                                       functionalities to manage the fares and
                                       the policies of the company.
  \item \textbf{Maintenance Interface}: This interface provides the maintenance
                                        staff with all the information about
                                        malfunctioning or ordinary maintenance
                                        needed by cars and charging plugs.
  \item \textbf{Cars Data Interface}: This is the interface that serves all the
                                      datas that the sensors installed on the
                                      cars read and send to the system.
  \item \textbf{Locking System Interface}: This interface is used for the
                                           communications between the
                                           application and the car locking
                                           system. It is used to send the
                                           locking and unlocking signal, to
                                           alert the system if the doors are not
                                           closed, and to transmit the unlocking
                                           code inserted by the user on the
                                           keyboard placed on the car's door.
  \item \textbf{Cars Management Interface}: This is the interface used by an
                                            administrator user in order to
                                            manage the car fleet of the company.
                                            Cars can be added or removed, and
                                            the state of a car can be changed
                                            manually in case of malfunctioning
                                            of the automated system.


\end{itemize}
