\subsection{Technical Risks}

Following is a list of possible technical risks in which we may incur during the
realization of the project.

\begin{description}
	\item [Losing source code: ] This problem is easily resolved due to the large
    amount and high reliability of versioning systems available on the market.
  \item [Infrastructure downtime: ] The availability of the system is strictly
    related to the company we rely on for the cloud infrastructure, an in depth
    search of the different proposals on the market can avoid this problem.
  \item [Failure on component integration: ] The failure of an integration test
    on a component can force the team to rewrite a large amount of code with a
    consequent loss of time. In order to avoid this kind of problems we need to
    precisely specify the interface of each component and we should also run
    integration test in an early stage of the creation of the component using
    stubs and drivers.
  \item [Code unreadability: ] This problem may often occur in a young and
    unexperienced team. To avoid this to happen is sufficent to apply the rules
    of good coding and to regularly inspect your work.
  \item [Delays in the delivery of external resources: ] This is another
    unpredictable problem that may occur, in our case, if the society providing
    the cars for our service cannot deliver the cars in time. A reactive action
    to this problem will be of no use, in fact the only solution is to
    preventively take into account this problem and schedule the delivery of the
    cars with enough room to compensate any problem.
  \item [Changes in the external services used in the project: ] Any change to
    the external services used inside our project can lead to a substantial
    review of the implementation of the whole system. This problem does not
    depend in any way from our company, and the only solution we have is to
    preventively search in the market of backup solutions for each of the
    external service used, and to write portable and reusable code.
\end{description}
