\subsection{Elements to be Integrated}

In the following, the system's elements to be integrated are spotted and
described. With \textit{elements} here we mean the subsystems composing the
system's design. The description of a subsystem is recursive, meaning that if a
subsystem is composed by other subsystems, even these are described. Description
of atomic components is avoided since are well described into the DD.

The main \textit{elements} composing our system are:
\begin{itemize}
  \item \textbf{Data Tier:} This element represents the DBMS. Even though we are
                            not developing the DBMS itself, it is still part of
                            the system, hence it has to be integrated.
  \item \textbf{Business Logic:} This element contains all the application
                                 logic present in our system. The main
                                 components of this element are: the
                                 \textbf{Authentication Manager}, the
                                 \textbf{Account Manager}, the
                                 \textbf{Maintenance Manager}, the
                                 \textbf{Vehicle Manager} and the
                                 \textbf{Reservation Manager}.
  \item \textbf{Web Server:} This is the element responsible for the
                             communications between the business logic tier and
                             the clients. It exposes a RESTful implementation
                             of the communication interfaces.
  \item \textbf{Client:} This element contains the three different kind of
                         clients that can access our application, namely the
                         \textbf{mobile client}, the
                         \textbf{web application client} and the
                         \textbf{car central system}
\end{itemize}

Every component that forms the different \textit{elements} has aledy been tested
individually, the tests to be performed are applied to the interfaces that
connect a component with another one.
