\subsection{\textcolor{blue}{HumanResEvents} Class}

\begin{enumerate}
	\item \textbf{C1} The class name does not suggest its purpose of supporting
		the creation of the category tree.

	\item \textbf{C1} Class attributes \textcolor{blue}{module} and
		\textcolor{blue}{resourceError} does not respect the naming convention for
		class attributes.

	\item \textbf{C1} The variables \textcolor{blue}{josonMap} declared at
		\textbf{L.126} and at \textbf{L.184} are probably misspelled and should be
		called \textcolor{blue}{jsonMap}.

	\item \textbf{C18} Any comment is used to explain the utility and purpose of
		the class.

	\item \textbf{C23} Actually, the javadoc for this class is empty, making hard
		the task to understand the purpose of the class and of its methods.

	\item \textbf{C27} The lines from \textbf{L.42} to \textbf{L.47} are
		identically repeated in other two methods
		(\textcolor{blue}{getCurrentEmployeeDetails} \&
		\textcolor{blue}{getChildComps}). It would be a possible to create a proper
		method to handle this assignments, avoiding code duplication.

	\item \textbf{C27} The lines from \textbf{L.126} to \textbf{L.129} are
		identically repeated in other two methods (\textcolor{blue}{getChildComps}
		\& \textcolor{blue}{getEmployeeInCompo}). It would be a possible solution to
		create a proper method to handle this assignments, avoiding code duplication.

	\item \textbf{C27} The lines \textbf{L.110-120} are repeated in another method
		(\textcolor{blue}{getChildComps}). It would be a possible to create a proper
		method to handle this assignments, avoiding code duplication.

	\item \textbf{C27} The lines \textbf{L.131-148} are repeated in other two
		methods (\textcolor{blue}{getChildComps},
		\textcolor{blue}{getEmployeeInComp}). It would be a possible solution to
		create a proper method to handle this assignments, avoiding code duplication.

\end{enumerate}
