\section{ALGORITHM DESIGN}

This sections present some of the main algorithms used in the application. Those algorithms are written
in a pseudocode resembling the java syntax.

\subsection{Available car search}
The following algorithm searches all the available cars near the area specified by the user, if a car
is within the visible area of the map, this function will place it on the map in the correct position
so that the user can possibly reserve it. Referring to the Google Maps API this function should be
added as a listener either to the "bounds\textunderscore changed" event and to the map generation event,
so that the user can drag the map and still see the available cars.

\begin{algorithm}
\begin{algorithmic}[1]
  \caption{\label{alg:stdreqhandler} Car Search Handling Algorithm}

  \Function{nearbyAvailableCarSearch}{}
    \State $ bounds = \textit{map.getBounds()} $
    \State $ availableCars = \Call {getAvailableCars} $
    \State $ i = \textit{0}$
    \For {$ i < \textit{availableCars.size()} $}
      \State $ currentLatLng = \textit{availableCars[i].getLatLng()} $
      \State $ currentId = \textit{availableCars[i].getId()} $
      \If {$ \textit{bounds.contains(currentLatLng)} $}
        \State \textit{map.addCar(
          \State position: currentLatLng,
          \State title: currentId,
          \State details: availableCars[i].getDetails()
        \State )}
      \ElsIf {$ \textit{map.contains(currentId)} $}
        \State map.removeCar(currentId)
      \EndIf
      \State $ i++ $
    \EndFor
    \State \textbf{return}
  \EndFunction

\end{algorithmic}
\end{algorithm}

\subsubsection{Functions and variables description}
\begin{itemize}
	\item \textbf{\textsc{getReservationLock}(CarId, User)}: Function that tries to acquire the lock on the
                                                           reservation part of the Car object and the
                                                           user object identified by the parameters
                                                           \textit{CarId} and \textit{User}.
                                                           If it can't get the lock after a certain
                                                           amount of time the function throws a
                                                           \textit{LockTimeoutException}.
	\item \textbf{\textsc{getCar}(CarId)}: Function that returns the Car object identified by the
                                         \textit{CarId} parameter.
                                         If no car corresponding to the specified ID is found, the
                                         function throws a \textit{CarNotFoundException}.
	\item \textbf{Car.isAvailable()}: Method that returns \textit{True} if the car on which it is called
                                    is currently available, returns \textit{False} instead.
	\item \textbf{Car.reserveCar()}: Method that set the state of the car on which it is called to
                                   \textit{Reserved}.
                                   This method is subject to the \textit{ReservationLock} obtainable
                                   through the \textit{\textsc{getCarReservationLock(CarId)}} function.
	\item \textbf{User.hasActiveReservation()}: Method that returns \textit{True} if the user on
                                                       which it is called on already has an active
                                                       reservation, returns \textit{False} instead.
	\item \textbf{ReservationTimer(minutes)}: This timer expires after the amount of minutes defined by the
                                            parameter \textit{minutes}, once expired it deletes the
                                            reservation it is associated to.
	\item \textbf{\textsc{reservation\textunderscore timer}}: Variable containing the duration of the
                                                            \textit{ReservationTimer} expressed in
                                                            minutes.
  \item \textbf{\textsc{createReservation}(CarId, User, ReservationTimer)}: Function that creates the
                                                                            reservation, associating the
                                                                            car, the user and the timer
                                                                            it gets as parameters.
                                                                            Among other things, it is
                                                                            in charge of setting the car
                                                                            as \textit{Reserved}, and
                                                                            starting the \textit{Timer}.
                                                                            The methods called in this
                                                                            function are subject to
                                                                            the \textit{ReservationLock}
                                                                            obtainable through the
                                                                            \textit{\textsc{getReservationLock}(CarId, User)}
                                                                            function.
	\item \textbf{Lock.releaseLock()}: Function that releases the lock on which it is called.
\end{itemize}

\pagebreak

\subsection{Car reservation}
The following algorithm takes care of the reservation of a car by a user. In order to avoid consistency
issues we need to ensure the atomicity of the reservation so that a car cannot be reserved by more than
one user. To do so we decided to use a lock-like pattern.


\begin{algorithm}

  \algblock[TryCatchFinally]{try}{endtry}
  \algcblock[TryCatchFinally]{TryCatchFinally}{finally}{endtry}
  \algcblockdefx[TryCatchFinally]{TryCatchFinally}{catch}{endtry}
  	[1]{\textbf{catch} #1}
  	{\textbf{end try}}

\begin{algorithmic}[1]
  \caption{\label{alg:stdreqhandler} Car Reservation Handling Algorithm}

  \Function{carReservation}{carId, user}
    \State $ reservationLock = null $
    \State $ car = null $
    \try
      \State $ reservationLock = \Call {getReservationLock}{carId, user} $
      \State $ car = \Call {getCar}{carId} $
      \If {$ !car.isAvailable() $}
        \State {\textbf{Throw} carNotAvailableException}
      \EndIf
      \If {$ user.hasActiveReservation() $}
        \State {\textbf{Throw} multipleReservationException}
      \EndIf
      \State $ reservationTimer = Timer $(\textsc{reservation\textunderscore timer})
      \State \Call {createReservation}{carId, user, reservationTimer}{$ $}
      \State $ ReservationLock.releaseLock() $
    \catch {(LockTimeoutException, carNotAvailableException)}
      \State {\textbf{return} ReservationError}
    \catch{(CarNotFoundException, multipleReservationException)}
      \State $ reservationLock.releaseLock() $
      \State {\textbf{return} ReservationError}
    \endtry
    \State \textbf{return}
  \EndFunction

\end{algorithmic}
\end{algorithm}

\subsubsection{Functions and variables description}
\begin{itemize}
	\item \textbf{map}: Variable referencing the map object created using the Google Maps API.
	\item \textbf{Map.getBounds()}: Method of the \textit{map} object that returns an object describing
                                  the boundaries of the currently visible map.
	\item \textsc{\textbf{getAvailableCars()}}: Is a function that returns a list of car objects
                                              containing all the currently available cars.
	\item \textbf{List.size()}: Method that returns the number of elements contained in the list on which
                              it is called.
	\item \textbf{Car.getLatLng()}: Method that returns a variable containing the current latitude and
                                  longitude of the car on which it is called.
	\item \textbf{Car.getId()}: Method that returns the identification code of the car on which it is
                              called.
	\item \textbf{Bounds.contains(LatLng)}: This method returns true in the case in which the
                                          geographical position described by its argument
                                          \textit{LatLng}, is inside the boundaries defined by
                                          the \textit{bounds} object on which the method is called.
	\item \textbf{Map.addCar(CarMarker)}: This method adds the \textit{CarMarker} object that receives
                                        as a parameter to the map on which it's called, making the car
                                        and all its informations visible on the map, and allowing the
                                        user to reserve it.
	\item \textbf{CarMarker}: Object containing the all the necessary informations concerning the car.
	\item \textbf{Map.removeCar(CarId)}: Method that removes the car identified by the \textit{CarId}
                                       parameter from the map on which it is called.
\end{itemize}

\pagebreak
