\subsubsection{External Inquiries}

\begin{itemize}
	\item \textbf{Retrieve reservation history}: the retrieve of the full reservation history (or part of it) is an operation that involves only two internal logic files, namely the reservation informations and the vehicle informations ILF.

	\item \textbf{Retrieve account informations}: operation involving either the user account informations ILF or the operator ILF.

	\item \textbf{Retrieve vehicle list}: simple operation involving the vehicle informations ILF.

	\item \textbf{Retrieve vehicle informations}: the characteristic informations regarding a vehicle are retrieved inquiring solely the vehicle informations ILF.

	\item \textbf{Retrieve vehicle status}: the informations regarding the current status of a specific vehicle are stored into the vehicle informations ILF.

	\item \textbf{Retrieve current reservation informations}: operation similar to the reservation history retrive operation. The same ILF are involved.

	\item \textbf{Retrieve area list}: simple inquire involving the area informations ILF.

	\item \textbf{Retrieve specific area informations}: as the previous operation, this one is simple as well and involves the same ILF.

	\item \textbf{Retrieve mantainance operator list}: only the operator ILF is involved in this operation.

	\item \textbf{Retrieve mantainance task list}: simple inquire operations regarding the mantainance task informations ILF.

	\item \textbf{Retrieve policy list}: the retrieval of the total list of policy rules present into the system or part of them is a simple operation involving the policy ILF.

	\item \textbf{Retrieve policy rule informations}: the informations regarding a specific policy rule involves the querying of the policy ILF.

	\item \textbf{Retrieve vehicles in specific area}: the achievement of this operation is reached through the querying of the vehicle informations ILF. 
\end{itemize}

\begin{table}[h!]
        \centering
        \begin{tabular}{  c | c | c | c |}
                \cline{2-4}
                & \multicolumn{3}{ c |}{Data elements} \\
                \cline{1-4}
                \multicolumn{1}{ | c | }{FRT} & 1 $\rightarrow$ 5 & 6 $\rightarrow$ 19 & 20+ \\
                \hline
                \multicolumn{1}{ | c | }{0-1} & Low & Low & Average \\ \hline
                \multicolumn{1}{ | c | }{2-3} & Low & Average & High \\ \hline
                \multicolumn{1}{ | c | }{4+} & Average & High & High \\
                \hline
        \end{tabular}
        \caption{EQ and EO's rating table}
        \label{table:EQRT}
\end{table}

\begin{table}[h!]
        \centering
        \begin{tabular}{ | c | c | c |}
                \hline
                \textbf{EQ} & \textbf{Complexity} & \textbf{Weigth} \\
                \hline
                Retrieve reservation history & Low & 3 \\
                Retrieve account informations & Low & 3 \\
                Retrieve vehicle list & Low & 3 \\
                Retrieve vehicle status & Low & 3 \\
                Retrieve current reservation info & Low & 3 \\
                Retrieve area list & Low & 3 \\
                Retrieve specific area info & Low & 3 \\
		Retrieve mantainance operator list & Low & 3 \\
		Retrieve mantainance task list & Low & 3 \\
		Retrieve policy rule list & Low & 3 \\
		Retrieve policy rule info & Low & 3 \\
                Retrieve vehicle in specific area & Low & 3 \\
                \hline
                \textbf{Partial Function Point} & \multicolumn{2}{c |}{36} \\
                \hline
        \end{tabular}
	\caption{EQ's PFP table}
	\label{table:EQPFP}
\end{table}

